I would like to thank Prof. N. Phuan Ong first and foremost for his patience and detailed advice during my PhD study. When I came to Princeton, I didn't have a clear idea about how to conduct cutting-edge research. It is Prof. Ong who spent a lot of time guiding me through the research process and helped me develop feasible ideas. He has an enormous amount of great research ideas that can push forward the research edge. He also taught me plenty of theoretical and experimental knowledge so that I can find the tools needed for my projects. I cannot express how much gratitude I owe him.

Besides, I am grateful for all the help I have received from my lab colleagues Joseph Checkelsky, Dongxia Qu, Tian Liang, Max Hirschberger, Minhao Liu, Yongkang Luo, Stephen Rowley, Wudi Wang and Tong Gao for their great help during my PhD study. In particular, I thank Joseph Checkelsky and Dongxia Qu for teaching me the sample mounting method, measurement techniques and cryogenics from the beginning. I also benefit a lot from my collaborators from Cava lab in chemistry department, including Satya Kushwaha, Shuang Jia, Jason Krizan, Quinn Gibson, Ni Ni and Yew San Hor. They not only have provided me with numerous high-quality crystals, but have also taught me all the steps to grow them. More importantly, I owe my gratitude to Prof. Robert Cava, as he allows me to try different things in his lab and never gets angry when I break his instruments. Without them, I can not carry out my experiments.

I also hope to thank Prof. Ali Yazdani, Prof. B. A. Bernevig, Prof. M. Zahid Hasan and Prof. Jason Petta for all the discussions about my research projects. I am thankful to Ilya Drozdov, Aris Alexandradinata, Andras Gyenis, Suyang Xu, Zhijun Wang, Yangle Wu and Loren Alegria for the discussions on both condensed matter physics and experimental techniques. I also thank Prof. David Huse for being the second reader of my thesis despite his busy schedule. 

The staff in the physics department cannot be more supportive. I thank James Kukon and Geoff Gettelfinger for providing liquid helium whenever it is needed. I also received a lot of help from the purchasing department, i.e. Ted Lewis, Soonoo Aria and Claude Champagne. Darryl Johnson helped me with all kinds of shipment. I am grateful to Catherine Brosowsky, Jessica Heslin and Barbara Grunwerg for all the administration work. Besides,  Bert Harrop, Pat Watson, Joe Palmer and Yong Sun instructed me on how to use the equipments in the clean room. I also appreciate the instructions from Steven Lowe in the machine shop. I hope to thank the staff scientists from the National High Magnetic Field Laboratory (NHMFL), such as Eun Sang Choi and Tim Murphy. Without them, I won't be able to conduct my experiments in a high magnetic field.

Lastly, I would like to thank my parents and all my friends, who have provided me a lot of help and support in every aspect of my life. 
