\chapter{Introduction\label{ch:intro}}

Since the introduction of the Berry phase into the study of condensed matter physics, mathematical concepts such as Chern numbers and the Gauss-Bonnet theorem have been widely used in describing the topology of the momentum space of Bloch electrons in a crystal. This theoretical advance has resulted in new ways to describe, classify and study the solids. Such classification typically leverages a topological order that depends on the integration of Berry curvatures in the whole Brillouin zone instead of only focusing on the local property of the wave function. As a result, many novel phases of matter have been found such as topological insulators, Chern insulators, Dirac semimetals and Weyl semimetals. These new classes of matter not only provide us a new perspective to view the crystals, but also can be used to imitate some mysterious phenomena in high energy that has been under search for a long time, such as axion electrodynamics, Majorana fermions, and the chiral anomaly effect. In addition, these new concepts could be of great value in applications. For example, the dissipationless edge states in of a Chern insulator have been proposed to construct the conducting channels in future integrated circuits to solve the Joule heating problem in the conducting wires. Besides, there are many theoretical proposals that leverage Majorana fermions built from TIs to form the quantum bit of a topological quantum computer in the future. Such applications will need a complete and detailed experimental study of the topological materials. In this introduction, we will briefly introduce both the theoretical and experimental progress in the investigation of TI, DSM and WSM in recent years. Then in later chapters we will describe the progress we have made in this area in the last few years.

%add formula for Berry phase, citations needed.

\input{ch-intro/TI}
\input{ch-intro/3D_Dirac}