
\chapter{Experimental Setup\label{ch:expsetup}}

In this chapter, we will briefly discuss some details of the transport techniques we use in our study of the topological insulators and Dirac semimetals. The research work in this thesis heavily depends on the magnetoresistance data at low temperatures. Hence I will first introduce the systems we use for our magnetoresistance and Hall measurement. Besides, we have developed the ionic liquid gating technique to tune the chemical potential in the TI experiments. Ionic liquid turns out to be a powerful dielectric material for gating semiconductors with a flat surface, such as TIs. But it also takes a large amount of effort to avoid chemical contamination and to obtain strong and robust results from the ionic liquid gating method. We will discuss our ways of using the ionic liquid on TIs. At the end of this chapter, we will introduce our method to protect and measure the air-sensitive Na$_3$Bi crystals. As we discussed in the previous chapter, Na$_3$Bi has two 3D Dirac nodes inside, and serves as a platform to study the long-sought Weyl physics. Unfortunately, due to the strong metallicity of Na atoms, Na$_3$Bi crystals are prone to oxidization by any amount of oxygen or water. Therefore, it takes enormous effort to preserve the Na$_3$Bi samples during the contact mounting process and the measurement process.

% include other files for sections of this chapter. These use the 'input' command since each section within a chapter should not start a new page.
% If you want to swap the order of sections, it is as simple as reversing the order you include them. 
\input{ch-expsetup/magnet}
\input{ch-expsetup/ionicliquid}
\input{ch-expsetup/airsensitive}
