
\chapter{Tuning the Surface Chemical Potential in Bi$_2$Te$_2$Se by Ionic Liquid Gating Method\label{ch:liquid}}

As we have discussed in previous chapters, it is of great practical value to increase the surface contribution in TI's conductance. Besides, there are many theoretical proposals such as building Chern insulators based on TIs, which require a chemical potential to be at the Dirac point. Thus it needs us to tune the chemical potential into the bulk band gap and close to the surface Dirac point. As a result, there has been a great amount of work trying to tune the chemical potential in TIs\cite{Checkelsky_gating, PabloBi2Se3, SacepeGate, PabloFilm, FuhrerBi2Se3, Checkelsky_liquid, IwasaMBE, Ando_liquid}.

Typically there are two methods to tune the chemical potential. One is to use the chemical doping method and one is to leverage a gating technique. Since there are few states (including the impurity states) inside the band gap, the chemical doping method may cause a large change in the carrier density and it is easy for the chemical potential to move across the band gap. Besides, the dopants introduce extra defects that can act as scattering centers and decrease the mobility of the sample. Therefore, it is favorable to use the gating method to fine tune the chemical potential in TI samples. 

Several groups\cite{Checkelsky_gating, PabloBi2Se3, SacepeGate, PabloFilm} have used the solid-state gating method to tune the chemical potential in different TIs. In many of these experiments, the quantum oscillations from the surface states on TIs are absent or very tiny, possibly due to the damage on the surface during the lithography process. Therefore the surface contribution in these samples is neither large nor of high quality, and the properties of the surface Dirac electrons at different $E_F$ remain to be explored.

Together with our group, some groups\cite{Yuan2011, FuhrerBi2Se3, Checkelsky_liquid, IwasaMBE, Ando_liquid} started to use another novel gating method, i.e. ionic liquid gating, to tune the chemical potential in TI crystals. Ionic liquid is composed of free-moving cations and anions. Hence, when a sample is immersed inside the ionic liquid and an electric voltage is applied, ions inside the liquid will move and one type of ions will pack on the surface of the sample and generate a large electric field on the sample surface. Besides, when the liquid is cooled down and becomes a solid, the ions are frozen and stay at the same position, maintaining the same electric field on the sample. Also, since the thickness of the ion layer on the sample is on the atomic scale, the electric field is very large and thus it can change the carrier density by a large amount. Such a powerful gating effect has been proved on many different materials, such as ZnO\cite{yuan2009ZnO}, ZrNCl\cite{ye2010liquid} and MoS$_2$\cite{YeMoS2}. We will show our results on tuning the surface chemical potential on Bi$_2$Te$_2$Se with the ionic liquid in this chapter.

% include other files for sections of this chapter. These use the 'input' command since each section within a chapter should not start a new page.
% If you want to swap the order of sections, it is as simple as reversing the order you include them. 
\input{ch-liquid/gating}
\input{ch-liquid/analysis}
\input{ch-liquid/discussion}
