
\chapter{Shubnikov$-$de Haas oscillations in Bi$_2$Te$_2$Se\label{ch:bts}}

Although topological insulators are supposed to have an insulating bulk that does not conduct, previous transport experiments on the suggested TIs found that most of the TI materials have a large bulk conductivity due to the crystal defects and imperfection. For example, although Bi$_2$Se$_3$ and Bi$_2$Te$_3$ have a simple surface state and a large band gap (on the order of 0.3 eV), their bulk carrier densities can only be reduced to approximate $10^{18} cm^{-3}$ after a large amount of work. Furthermore, the chemical doping method that is used to reduce the carrier densities in Bi$_2$Se$_3$ and Bi$_2$Te$_3$ is likely to reduce to the surface mobility. As a result, the surface current is hard to detect and easily immersed in the overwhelming bulk current. The bulk carriers are usually caused by the intrinsic imperfection of the crystals. For instance, despite of extra Se pressure in the growing environment, a large number of Se vacancies can still be generated in Bi$_2$Se$_3$ and then lead to n-type carriers in the as-grown crystals. Meanwhile, Bi$_2$Te$_3$ is known to have Bi-Te anti-site defects that produce p-type carriers. 

Consequently, the metallic bulk has been a big obstacle to the study of new transport phenomena on TIs. Although there are many proposed transport experiments to search for novel physics on the surface of TIs, they depend on a high-quality surface current and the high carrier density in the bulk has severely hampered the progress. Therefore, it is important to reduce the bulk carriers in order to investigate the surface states on TIs. 

To overcome the difficulty, we grew various TI crystals to suppress the bulk carrier density. Among these crystals, one of the most promising ones is Bi$_2$Te$_2$Se. Since Bi$_2$Se$_3$ is n-type due to the Se vacancies and Bi$_2$Te$_3$ is p-type due to the Bi-Te anti-sites, we believe the combined Bi$_2$Te$_2$Se could have a charge compensation between the n-type and p-type carriers. As a result, Bi$_2$Te$_2$Se is likely to have much fewer bulk carriers. In addition, since Bi$_2$Te$_2$Se is a stoichiometric crystal, the surface mobility won't be sacrificed by the chemical dopants.

In this section,we will discuss our transport results on Bi$_2$Te$_2$Se, a TI compound with a large bulk resistivity (6 $\Omega$cm at 4 K). We have observed prominent Shubnikov-de Haas (SdH) oscillations in Bi$_2$Te$_2$Se, which could be used to detect the surface states out of the bulk signal. A fitting to the oscillations yields a surface mobility ($\mu_s\sim$ 2,800 cm$^2$/Vs), which is much larger than the bulk mobility ($\mu_b\sim$ 50 cm$^2$/Vs). These parameters indicate a high surface to bulk current ratio in Bi$_2$Te$_2$Se and it has a potential to serve as the platform TI material for searching Majorana fermions and  axion electrodynamics.

% include other files for sections of this chapter. These use the 'input' command since each section within a chapter should not start a new page.
% If you want to swap the order of sections, it is as simple as reversing the order you include them. 
\input{ch-bts/bts-band}
\input{ch-bts/result14T}
\input{ch-bts/result45T}
\input{ch-bts/summary}
